---
title: "session 3"
author: "martin"
date: "13/01/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}

library(tidyverse)
library(dplyr)
mobile<-read_csv("https://raw.githubusercontent.com/vmandela99/Class-assignment-12th-july-2019/master/mobilemoney_data.csv")

view(mobile)

library(skimr)
skimr::skim(mobile)
```


## show the number of accounts present
```{r}
mobile$account_type <- as.factor(mobile$account_type)
mobile%>%count(mobile$account_type)
```
## district that has many people
```{r}
mobile %>% count(mobile$district)
```
district c has the highest number of people


##percentage of people from district A with sacco account

```{r}
mobile %>% filter(district=="District_A") %>% count(district,account_type) %>% mutate(percent=n/sum(n)*100)

```
18.2% of people from district A have sacco account


##how many grades completed are there
```{r}
mobile$highest_grade_completed<-as.factor(mobile$highest_grade_completed)
mobile %>%count(highest_grade_completed)
```
15 grades completed

##largest weight in the survey
```{r}
 max(mobile$weight)
```
48.25 was the largest weigh trecorded


## percentage of people in the universsity with mobile money account
```{r}
mobile %>% filter(highest_grade_completed=="university") %>% count(highest_grade_completed,account_type) %>% mutate(percent=n/sum(n)*100)

```
32.4% of people in the university have mobile account

```{r}
library(ggplot2)
mobile %>% count(account_type) %>%mutate(account_type=fct_reorder(account_type,n)) %>%  ggplot(aes(x=account_type,y=n))+geom_col(fill="red")
```


```{r}
mobile %>% count(district) %>%mutate(district=fct_reorder(district,n)) %>%  ggplot(aes(x=district,y=n))+geom_col(fill="yellow")+coord_flip()
```

```{r}
library(ggthemes)
mobile %>% ggplot(aes(x=account_type,y=age))+geom_boxplot(fill="blue")+theme_economist()
```






